
# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
##install.packages("knitr")
##library("knitr")
#knit2html("PA1_template.Rmd")

data  <- read.csv("activity.csv")
#str(data)

data$interval <- as.factor(data$interval)
data_day_sum <- with(data,aggregate(steps,list(date=date),sum, na.rm=TRUE, nan.rm=TRUE))
data_day_mean <- with(data,aggregate(steps,list(date=date),mean, na.rm=TRUE, nan.rm=TRUE))
data_day_med <- with(data,aggregate(steps,list(date=date),median, na.rm=TRUE))

#Interval
interval <- with(data,aggregate(steps,list(interval=interval),mean, na.rm=TRUE, nan.rm=TRUE))
max <- max(as.numeric(interval$x))
max_interval <- subset(interval, x == max )
```
Frecuencia de pasos
```{r}
hist(data_day_sum$x)
```


## What is mean total number of steps taken per day?

##Steps each day
```{r}
data_day_sum
```
##Average steps
```{r}
data_day_mean
```
##Median steps
```{r}
data_day_med
```

## What is the average daily activity pattern?

```{r}
plot(interval$interval, interval$x, type="l",col="blue", ylab="Steps", main="", xlab="")
with(max_interval, lines(interval,x,col="red"))
```
###Max interval: 835


## Imputing missing values
##Replace with mean
```{r}
v_mean <- mean(data$steps, na.rm=TRUE)
data_original <- data
data[is.na(data)] <- v_mean
```

##Different histograms: More frecuency on "cleaned" data
```{r}
#Sum of cleaned data
data_day_sum_limpio <- with(data,aggregate(steps,list(date=date),sum, na.rm=TRUE, nan.rm=TRUE))
#Compare Histograms

par(mfrow = c(1,2))
hist(data_day_sum$x)
hist(data_day_sum_limpio$x)
```

##Missing values
```{r}
subset(data_original, is.na(steps))
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
#str(data)
data$weekday <- weekdays(as.Date(data$date))

data$weekday <- replace(data$weekday, data$weekday=="Monday", "weekday")
data$weekday <- replace(data$weekday, data$weekday=="Tuesday", "weekday")
data$weekday <- replace(data$weekday, data$weekday=="Wednesday", "weekday")
data$weekday <- replace(data$weekday, data$weekday=="Thursday", "weekday")
data$weekday <- replace(data$weekday, data$weekday=="Friday", "weekday")
data$weekday <- replace(data$weekday, data$weekday=="Saturday", "weekend")
data$weekday <- replace(data$weekday, data$weekday=="Sunday", "weekend")
#Convert to factor
data$weekday <- as.factor(data$weekday)
```
### More steps early in the morning on weekdays. More steps in the afternoon on weekend
```{r}
library(ggplot2)
par(mfrow = c(1,1))
qplot(interval, steps, data = data, facets = . ~ weekday, geom="line")
```



